---
title: "Market Segmentation"
output: github_document
---
```{r}
rm(list=ls())
df <- read.csv(file="C:\\Users\\ckraw\\OneDrive\\Desktop\\social_marketing.csv", header=TRUE, sep=",")
library(ggplot2)
library(dplyr)
library(purrr)
library(factoextra)
df=df[,-1]
```

In order to use k-means clustering on the twitter followers a value of k needs to be chosen. The elbow plot below is somewhat ambiguous as to where the elbow is, but a value of 7 was chosen for k.  

```{r}
set.seed(123)

# function to compute total within-cluster sum of square 
wss <- function(k) {
  kmeans(df, k, nstart = 15 )$tot.withinss
}

# Compute and plot wss for k = 1 to k = 15
k.values <- 1:15

# extract wss for 2-15 clusters
wss_values <- map_dbl(k.values, wss)

plot(k.values, wss_values,
       type="b", pch = 19, frame = FALSE, 
       xlab="Number of clusters K",
       ylab="Total within-clusters sum of squares")
```
```{r}
set.seed(123)
final <- kmeans(df, 7, nstart = 25)
```


```{r}
cluster=df %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("mean")

cluster
```

__Below we will examine the 7 customer segments that were identified using k-means clustering:__  

__Customer segment 1, Politics:__  
Looking at the mean values of customer segment 1 the categories that stand out are Travel, Politics, and News. These categories depict a customer base of individuals who follow world events and travel. 


__Customer segment 2, Fashion:__  
Looking at the mean values of customer segment 2 the categories that stand out are Photo Sharing, Music, Cooking, Beauty, and Fashion. These categories depict a customer base of individuals interested in fashion/beauty.


__Customer segment 3, Family:__  
Looking at the mean values of customer segment 3 the categories that stand out are Sports Fandom, Food, Religion, Family and Parenting. These categories depict a customer base of parents and family oriented individuals.


__Customer segment 4, Health Conscious:__  
Looking at the mean values of customer segment 4 the categories that stand out are Food, Health, Cooking, Outdoors, and Fitness. These categories depict a customer base of health conscious individuals.  


__Customer segment 5, College Students/Young Adults:__  
Looking at the mean values of customer segment 5 the categories that stand out are tv/Film, online gaming, College/Uni, and Sports Playing. These categories depict a customer base of college students/young adults.


__Customer segment 6, N/A:__  
Looking at the mean values of customer segment 6 no categories standout. This is a very uninterpretable customer segment and it is possible that this segment is a collection of customers from many segments. For every value of K, there was an uninterpretable segment.  



__Customer segment 7, Pop Culture:__  
Looking at the mean values of customer segment 7 the categories that stand out are Chatter, Current Events, Photo Sharing, and Shopping. These categories depict a customer base of pop culture influenced individuals.


